---
title: "Data Manipulation"
author: "Julia Thompson"
date: "9/19/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Import Datasets

```{r}
litters_data = read_csv("./data/FAS_litters.csv")
litters_data = janitor::clean_names(litters_data)

pups_data = read_csv("./data/FAS_pups.csv")
pups_data = janitor::clean_names(pups_data)
```

## Selecting

Selecting is literally only for changing/selecting the columns that you have.

```{r}
select(litters_data, group, litter_number) #what columns you want to select 

select(litters_data, litter_number, gd0_weight, starts_with("pups"))

select(litters_data, litter_number, group, gd0_weight)

select(litters_data, litter_number, group, everything()) #this takes litter number, group, and everything else

select(litters_data, -group) #this keeps everything except group

select(litters_data, litter_number, gd0_weight:pups_born_alive) #keep everything from gd0 weight to pups alive

select(litters_data, GROUP = group, litter_number) #you can also rename as part of this process

rename(litters_data, GROUP = group) #this just renames, it doesn't select

#you can use starts_with(), ends_with(), contains(), and type ?select_helpers
```

## Filtering

Double equals is a logical oprator. It asks a quesiton: are these two things equal? If so (true), keep it. Keeps the rows for which the logical quesiton is true.

Some ways to filter data:

*   gd_of_birth == 20

*   pups_born_alive >= 2

*   pups_survive != 4

*   !(pups_survive == 4)

*   group %in% c("Con7", "Con8")

*   group == "Con7" & gd_of_birth == 20

```{r}
filter(litters_data, group == "Con7") #is the value in group equal to this sepcific thing? 

filter(litters_data, gd_of_birth == 20)

filter(litters_data, gd_of_birth < 20)

filter(litters_data, pups_born_alive < 6)

filter(litters_data, pups_born_alive < 6, group == "Con7")

# filter(litters_data, group == "Con7" | group == "Mod8") #this does the same as the below code

filter(litters_data, group %in% c("Con7", "Mod8"))

filter(litters_data, gd0_weight + gd18_weight < 70)

# Don't do this:
# filter(litters_data, !is.na(gd0_weight))

#Do this:
drop_na(litters_data, gd0_weight)
```

## Mutate

```{r}
mutate(
  litters_data, 
  wt_gain = gd18_weight - gd0_weight,
  group = str_to_lower(group)) #this makes the string group all lower case
```

## Arrange

```{r}
arrange(litters_data, pups_born_alive)

arrange(litters_data, desc(pups_born_alive))

arrange(litters_data, pups_born_alive, gd0_weight)

```



